\vspace{-1cm}\Large{\textsf{The Size Distribution of Firms and Industrial Water Pollution: A Quantitative Analysis of China} \\ \textsf{Replication Instructions}}

### 2019-09-20 Documentation/Replication_Instruction.tex
daily sync

To replicate all the results in the paper, three softwares are used. Specifically, \textsc{Stata} is used for initial data processing. All the empirical results are then produced using \code{R}. MATLAB is used to compute all the quantitative results. There is no particular scientific reason that we use one statistical software (\textsc{Stata}) for data cleaning and the other (\code{R}) for empirical analysis.\footnote{Due to limited backward compatibility of \textsc{Stata} and that the \code{foreign} package of \code{R} supports only \code{.dta} files saved by \textsc{Stata} up to Version 12, to run the code without any modification, the reader would need \textsc{Stata} 12. Readers with more recent version of the \textsc{Stata} would need to either modify in the \code{.do} file everywhere \code{.dta} files are read and written, or use alternative \code{R} package (for instance \code{readstata13}) to convert the data in \bcode{cpsc\_convert.R} and \bcode{cec\_convert.R}. Compatibility of our code is not tested under such environments. However, none of our results should be affected though.} We do this simply because it is easier to handle Chinese characters with \textsc{Stata} while \code{R} switches back and forth between different datasets swiftly. Veterans of \textsc{Stata} (or \code{R}) should be able to replicate all the empirical results with just one software using our source code as reference with ease. In addition, which in fact should go without saying, for readers without a licence to MATALB, GNU Octave could be used instead.

@@

    Individual researchers not affiliated with the MEE and institutions under its direct supervision needs to submit the application through the official portal for Information Access (\begin{CJK}{GBK}{kai} 政府信息公开\end{CJK}) by the MEE at the following url: \url{http://www.mee.gov.cn/weihu/201706/t20170625_416641.shtml}. The url is retrieved on September 15th, 2019 and may vary in the future. All applications are subject to official approval by the General Office of Ministry of Ecology and Environment (\begin{CJK}{GBK}{kai}中华人民共和国生态环境部办公厅\end{CJK}).

    For an official introduction to the NGSPS and declassified information at the aggregated level, interested readers could refer to the book \textit{Data Collection of the National General Survey of Pollution Sources} (\begin{CJK}{GBK}{kai}《污染源普查数据集》, 中国环境科学出版社, 2011\end{CJK}), which is publicly available.
    \item
    The CNEC is also a confidential dataset belonging to National Bureau of Statistics of China. Many universities and institutions have legal copy of the dataset though. Our copy was obtained from Fudan University.
    \item
    The SUSB is publicly available from the Census Bureau's dedicated website. The url, retrieved on September 15th, 2019, and subject to possible change in the future, is \url{https://www.census.gov/programs-surveys/susb.html}.
\end{itemize}

In the replication files, we cannot provide micro-level data of the NGSPS and CNEC, due to non-disclosure agreements with the MEE and Fudan University. Therefore, we only post the source code that generates the results. However, to facilitate replication by the readers who have access to the datasets, we post the log files when running the analysis on our computer.

@@

The readers will get a number of files for replicating the results. To ease digestion, we briefly introduce the structure of the folders and files. As typographical convention, we use \bcode{blue computer modern typewriter} to indicate \bcode{folders} and \bcode{files}. The current folder is referred to as \bcode{./}.
\begin{itemize}
    \item
    \bcode{./Empirical/}:
    \begin{itemize}
        \item
        \bcode{./Data/}: contains the raw and cleaned data.
        \item
        \bcode{./Results/}: contains all the figures and log-files.
        \item
        \bcode{./cpsc\_raw.do}: does initial processing of the NGSPS.
        \item
        \bcode{./cec\_clean.do}: does initial processing of the CNEC.
        \item
        \bcode{./cpsc\_convert.R}: converts the NGSPS to binary format of \code{R}.
        \item
        \bcode{./cec\_convert.R}: converts the CNEC to binary format of \code{R}.
        \item
        \bcode{./Empirical\_AEJ.R}: produces most empirical results in the main text.
        \item
        \bcode{./Empirical\_Appendix.R} produces most empirical results in the appendices.
        \item
        \bcode{./Accounting.R}: executes the accounting exercise.
        \item
        \bcode{./Descriptive.R}: computes some summary statistics of the NGSPS.
    \end{itemize}
    \item
    \bcode{./Quantitative/}
    \begin{itemize}
        \item
        \bcode{./Results/}: contains all the results and figures.
        \item
        \bcode{./twosectors.m}: computes the equilibrium of the two-sector model with perfect substitution used in the main text and saves the results in \bcode{.mat} format.
        \item
        \bcode{./fcn2.m}: computes the excess demand at a given vector of price; called by \bcode{twosectors.m}.
        \item
        \bcode{./compute\_tables.m}: computes the raw data used to calculate Tables 4, 5 and 6 in the main text.
        \item
        \bcode{./plot\_figures.m}: plots Figures 4 and 5 in the main text.
        \item
        \bcode{./twosectors\_ces.m}: computes the equilibrium of the two-sector model with constant elasticity of substitution used in Appendix J and saves the results in \bcode{.mat} format.
        \item
        \bcode{./fcnces.m}: computes the excess demand at a given vector of price; called by \\
        \bcode{twosectors\_ces.m}.
        \item
        \bcode{./compute\_tables\_ces.m}: computes the raw data used to calculate Tables J.1 in Appendix J.
        \item
        \bcode{./misc.m}: draws Figure D.2 and computes the decomposition in Sections \rom{4}.A and \rom{4}.B of the main text.
    \end{itemize}
\end{itemize}

@@

The NGSPS comes by 5 \textsc{Stata} \code{.dta} files. \bcode{keynum.dta} contains information of the key sources, while \bcode{reg1.dta} to \bcode{reg4.dta} host information of the regular sources. There are 4 files for the regular sources because of the technical limitation back when we initially applied for the data. It is likely that the reader will get one file for the regular source at this moment. These files should be placed under \bcode{./Empirical/Data/}. Executing \bcode{cpsc\_raw.do} will combine the four \bcode{regx.dta} to \bcode{regall.dta} and label all the variables in \bcode{keynum.dta} and \bcode{regall.dta}. It also generates another file \bcode{allfirms.dta} where the two files are combined. All three files are saved under \bcode{./Empirical/Data/}.

Our copy of the CNEC has two \textsc{Stata} \code{.dta} files. \bcode{cec2004\_large\_full.dta} holds those samples that overlap with the commonly used 2004 Annual Surveys of Industrial Firms, while \bcode{cec2004\_small.dta} contains small firms not surveyed in the annual ASIF. Again, they should be placed under \bcode{./Empirical/Data/}. The file \bcode{cec\_clean.do} labels all the variables. Upon completion, the original un-labeled files will be replaced by files of the same name.

With these two steps completed, the reader needs to convert the data from \textsc{Stata} \code{.dta} to the internal binary \code{R} format \code{.RData}. File \bcode{cpsc\_convert.R} converts \bcode{keynum.dta} to \bcode{KEYFIRM\_R.RData}, \bcode{regall.dta} to \bcode{REGFIRM\_R.RData} and \bcode{allfirms.dta} to \bcode{ALLFIRM\_R.RData}. Similarly, \bcode{cec\_convert.R} converts \\ \bcode{cec2004\_small.dta} to \bcode{DSMALL\_R.RData}, \bcode{cec2004\_large\_full.dta} to \bcode{DLARGE\_R.RData}. It then extracts only the variables used in the paper and combines the two \code{.RData} files to one file \bcode{CNEC\_avgp.RData}. All the files are saved under \bcode{./Empirical/Data/} as before.

@@

In what follows, we will only be using the files converted by \code{R}. A list of the essential files is provided below. All the files should be placed under \bcode{./Empirical/Data/}. For ease of reference, we use the two-letter acronyms in parenthesis when referring to the data files later.
\begin{itemize}
    \item
    \bcode{KEYFIRM\_R.RData (PK)}: Key sources of the NGSPS.
    \item
    \bcode{ALLFIRM\_R.RData (PA)}: All sources of the NGSPS.
    \item
    \bcode{CNEC\_avgp.RData (CA)}: All samples in the CNEC.
    \item
    \bcode{DLARGE\_R.RData (DL)}: A subset of \code{CA} which overlaps with the 2004 Annual Surveys of Industrial Firm.
    \item
    \bcode{susb04.csv (US)}: SUSB 2004.
\end{itemize}

@@

We try to organize our source code by sections in the paper as much as we can. This is not always possible though (or creates unnecessary confusion). We do, however, break the code by sections within the file, where tasks that are reasonably connected logically are grouped together. The code is written such that each section is self-contained, so the readers do not have to run from the very beginning if she/he only wants to replicate a certain result.\footnote{That said, the readers should always check to ensure that all the functional packages of \code{R} are loaded.} Table \ref{tab:navi_main} summarizes the correspondence between the results in the paper (tables, figures, regression results, in-text numbers, etc.) and the section of code files that computes them, as well as data dependency. To further assist the readers to visually navigate through the code, important sections are always indicated by a 76-character line of \code{=}. This is the longest line in all the source code, and should be those most visually noticeable amongst all.

@@

    Table 1 is produced by the first part of \bcode{Descriptive.R}. All the numbers are printed to the terminal. Row 1 comes first, with Rows 2 and 3 follow.

@@

    Regressions (2), (3), and the un-numbered one in Section \rom{1}.B part \textit{The Role of End-of-pipe Treatment Technologies}, as well as Table 2 are produced by Section 2 of \bcode{Empirical\_AEJ.R}. As one exception, Section 2 relies on Section 1 of \bcode{Empirical\_AEJ.R}. The information in Table 2 is printed to the terminal in the order of Columns 2, 1, 3 and 4. The numbers in Columns 1 and 2 are directly taken from the output. Columns 3 and 4 are calculated by normalizing the physical equipment level to 100. Regression results are then printed to the terminal. First is the unnumbered regression, with those of Regressions (2) and (3) follow in order.

@@

    The in-text number of the accounting exercise can be calculated from the results following executing \bcode{Accounting.R}. The 33\% reduction in the last paragraph of Section \rom{1}.C part \textit{An Accounting Exercise} can then be calculated as the weighted average of the variable \bcode{ppar} with Row 1 of Table 1 as the weight. Notice that the variable \bcode{ppar} is exactly Row 3 of Table F.1. Because according to Row 1 of Table 1, the five industries combined contribute to 77\% of total COD emission, assuming that industries emitting the other 23\% COD remain intact, the 25\% reduction in average intensity is simply calculated as $1 - (67\% \times 77\% + 100\% \times 23\%) \triangleq 25\%$.

@@

    To compute the quantitative results, the reader would need to execute \bcode{twosectors.m} several times. There are four cases to be computed: the benchmark case, the no distortion case, the regulation case and the flat tax case. The reader need to manually set the parameters in \bcode{twosectors.m} for each cases, namely the distortions \code{tauzd, tauzc}, the regulation intensity \code{xi} and the file name at the very end. The code is set to compute and save the benchmark results initially. The code contains all the relevant statements. The readers only need to comment and un-comment the relevant sections, which should be very easy to locate by searching for the variable name.

@@

        Execute \bcode{twosectors.m}. Some information would be printed to the terminal. Please refer to the log file \bcode{twosectors\_log.pdf} for details. The results are saved in \\ \bcode{./Quantitative/Results/benchmark\_new.mat}.

@@

        Set \code{tauzd} and \code{tauzc} to the benchmark level, change \code{xi} to 0.355, and the export destination to \bcode{./Results/regulation\_new.mat}. The results will be saved in this file after execution. This case is labeled as Case (ii) in the paper.

@@

        Set \code{tauzd} and \code{tauzc} to the flat tax level, reverse \code{xi} back to 0.23, and the export destination to \bcode{./Results/flattax\_new.mat}. The results will be saved in this file after execution. This case is labeled as Case (i') in the paper.

@@

    Tables 4, 5 and 6 are calculated using the output of \bcode{compute\_tables.m}. Notice that Tables 4 and 6 are presented in relative changes and share a similar structure. By changing the input files at the beginning of \bcode{compute\_tables.m} (in particular the 4 \code{.mat} just computed), \bcode{compute\_tables.m} prints the raw data of the corresponding entries in the same structure as the tables in the paper. Table 5 can be directly taken from the output \code{Table 5} of executing \bcode{compute\_tables.m} with the input being the corresponding cases. Entries in Table 4 can be calculated from the \code{Table 4} of the benchmark case and Cases (i) and (ii), while that of Table 6 can be calculated from \code{Table 4} of the benchmark case and Case (i'). The calculations of the relative changes are not automated, and the readers do have to do the calculations manually as we did. We apologize for the inconvenience. The in-text decomposition of the total reduction to the contribution of size distribution and technology adoption can be performed using \bcode{misc.m}. The readers need to change the second input file to either \bcode{notax\_new.mat} or \bcode{regulation\_new.mat}, depending on the cases to compute. The role of technology adoption is printed to the terminal, with the residual being that from the size distribution.
    Several calibration targets are computed from the data as well. This last bulletin explains where they are computed.
    \begin{itemize}
        The share of firms using clean technology 57\% is calculated in Section 2 of \bcode{Empirical\_AEJ.R}. The variable \code{clean\_share} hosts the number.
        The average adoption cost of clean technology as a ratio of output for clean firms 2.5\% is calculated at the end of Section 2 of \bcode{Empirical\_AEJ.R}. The number is printed to the terminal directly.
        The value of $\phi_1$ is computed in the first part of Section 4 of \bcode{Empirical\_AEJ.R}. The variable \code{phi\_quant} carries the information.
        The firm size and employment distributions [the light (yellow) bars in Figure 5] are computed at the end of Section 3 of \bcode{Empirical\_AEJ.R}. The variable \code{distchn} is first used to save the employment distribution and then the firm size distribution.
    \end{itemize}

@@

\begin{table}[t]
\footnotesize
\centering
\begin{threeparttable}
\caption{Navigating the Appendix}
\begin{tabular}{llll}
    \hline \hline
    Content                         & File Name                       & File Dependency          & Location in Code \\
    \midrule
    \textbf{Appendix A.1} \\
    \ \ \ Table A.1                 & \bcode{Descriptive.R}           & \code{PK, PA} \\
    \textbf{Appendix B} \\
    \ \ \ Figure B.1                & \bcode{Empirical\_Appendix.R}   & \code{PK, PA, DL, CA}    & Section 1  \\
    \textbf{Appendix C.1} \\
    \ \ \ Figure C.1                & \bcode{Empirical\_Appendix.R}   & \code{PK}                & Section 2  \\
    \ \ \ Table C.1                 & \bcode{Empirical\_Appendix.R}   & \code{PK}                & Section 2  \\
    \ \ \ Figure C.2                & \bcode{Empirical\_Appendix.R}   & \code{PK}                & Section 2  \\
    \ \ \ Regressions (!\#)         & \bcode{Empirical\_Appendix.R}   & \code{PK}                & Section 2  \\
    \ \ \ 3-Regressions (!\#)       & \bcode{Empirical\_AEJ.R}        & \code{PK}                & Section 2 \\
    \textbf{Appendix D.1} \\
    \ \ \ Figure D.1                & \bcode{Empirical\_Appendix.R}   & \code{CA}                & Section 4  \\
    \ \ \ Figure D.2                & \bcode{misc.m}       \\
    \textbf{Appendix D.2} \\
    \ \ \ Table D.1                 & \bcode{Empirical\_Appendix.R}   & \code{PK}                & Section 3  \\
    \ \ \ Regression (!\#)          & \bcode{Empirical\_Appendix.R}   & \code{PK}                & Section 3  \\
    \ \ \ Fixed Cost Ratio          & \bcode{Empirical\_Appendix.R}   & \code{PK}                & Section 3  \\
    \textbf{Appendix E.1} \\
    \ \ \ Figure E.1                & \bcode{Empirical\_Appendix.R}   & \code{CA, US}            & Section 5  \\
    \textbf{Appendix F} \\
    \ \ \ Table F.1                 & \bcode{Accounting.R}            & \code{PK, CA, US}  \\
    \textbf{Appendix J} \\
    \ \ \ Table J                   & \bcode{twosectors\_ces.m}       & \multirow{2}{*}{\centering \code{*.mat}} \\
                                    & \bcode{compute\_tables\_ces.m} \\
    \bottomrule
\end{tabular}
\label{tab:navi_appendix}
\begin{tablenotes}
     \footnotesize{
     \item[$\dagger$]
     Acronyms for datasets:
     \begin{itemize}[leftmargin=*]
        \item
        \bcode{KEYFIRM\_R.RData (PK)}: Key sources of the NGSPS.
        \item
        \bcode{ALLFIRM\_R.RData (PA)}: All sources of the NGSPS.
        \item
        \bcode{CNEC\_avgp.RData (CA)}: All samples in the CNEC.
        \item
        \bcode{DLARGE\_R.RData (DL)}: A subset of \code{CA} which overlaps with the 2004 Annual Surveys of Industrial Firm.
        \item
        \bcode{susb04.csv (US)}: SUSB 2004.
     \end{itemize}
     }
     \item[$\ddag$]
     All the \code{*.mat} files will be produced by \bcode{twosectors\_ces.m}.
     \item[$\diamondsuit$]
     Notation (!\#) stands for ``un-numbered.''
\end{tablenotes}
\end{threeparttable}
\end{table}

>>>>

To replicate all the results in the paper, three softwares are used. Specifically, \textsc{Stata} is used for initial data processing. All the empirical results are then produced using \code{R}. MATLAB is used to compute all the quantitative results. There is no particular scientific reason that we use one statistical software (\textsc{Stata}) for data cleaning and the other (\code{R}) for empirical analysis.\footnote{Due to limited backward compatibility of \textsc{Stata} and that the \code{foreign} package of \code{R} supports only \code{.dta} files saved by \textsc{Stata} up to Version 12, to run the code without any modification, the reader would need \textsc{Stata} 12. Readers with more recent version of \textsc{Stata} would need to either modify in the \code{.do} file everywhere \code{.dta} files are read and written, or use alternative \code{R} package (for instance \code{readstata13}) to convert the data in \bcode{cpsc\_convert.R} and \bcode{cec\_convert.R}. Compatibility of our code is not tested under such environments. However, none of our results should be affected though.} Veterans of \textsc{Stata} or \code{R} should be able to replicate all the empirical results with just one software using our source code as reference with ease. In addition, it should go without saying that for readers without a licence to MATALB, GNU Octave could be used instead.

@@

    Individual researchers not affiliated with the MEE and institutions under its direct supervision need to submit the application through the official portal for requesting Information Access (\begin{CJK}{GBK}{kai} 政府信息公开\end{CJK}) by the MEE at the following url: \url{http://www.mee.gov.cn/weihu/201706/t20170625_416641.shtml}. The url is retrieved on September 15th, 2019 and may vary in the future. All applications are subject to official approval by the General Office of Ministry of Ecology and Environment (\begin{CJK}{GBK}{kai}中华人民共和国生态环境部办公厅\end{CJK}).

    For an official introduction to the NGSPS and declassified information at the aggregated level, interested readers could refer to the book \textit{Data Collection of the National General Survey of Pollution Sources} (\begin{CJK}{GBK}{kai}《污染源普查数据集》, 中国环境科学出版社, 2011\end{CJK}), which is publicly available. We provide a summary in English in Online Appendix A of our paper.
    \item
    The CNEC is also a confidential dataset belonging to National Bureau of Statistics of China. Many universities and institutions have legal copy of the dataset though. Our copy was obtained from Fudan University.
    \item
    The SUSB is publicly available from the Census Bureau's dedicated website. The url, retrieved on September 15th, 2019, and subject to possible change in the future, is \url{https://www.census.gov/programs-surveys/susb.html}.
\end{itemize}

In the replication files, we cannot provide micro-level data of the NGSPS and CNEC, due to non-disclosure agreements with the MEE and Fudan University. Therefore, we only post the source code that generates the results. However, to facilitate replication by the readers who have access to the datasets, we post the log files when running the analysis on our computer. More details on the log files are provided at the end of this note.

@@

The readers will get a number of files for replicating the results. To ease digestion, we briefly introduce the structure of the folders and files. As typographical convention, we use \bcode{blue computer modern typewriter} to indicate \bcode{folders} and \bcode{files}. The parent folder is referred to as \bcode{./}.
\begin{itemize}
    \item
    \bcode{./Empirical/}:
    \begin{itemize}
        \item
        \bcode{./Data/}: contains the raw and cleaned data.
        \item
        \bcode{./Results/}: contains all the figures and log-files.
        \item
        \bcode{./cpsc\_raw.do}: does initial processing of the NGSPS.
        \item
        \bcode{./cec\_clean.do}: does initial processing of the CNEC.
        \item
        \bcode{./cpsc\_convert.R}: converts the NGSPS to the binary format of \code{R}.
        \item
        \bcode{./cec\_convert.R}: converts the CNEC to the binary format of \code{R}.
        \item
        \bcode{./Empirical\_AEJ.R}: produces most empirical results in the main text.
        \item
        \bcode{./Empirical\_Appendix.R} produces most empirical results in the appendices.
        \item
        \bcode{./Accounting.R}: executes the accounting exercise.
        \item
        \bcode{./Descriptive.R}: computes some summary statistics of the NGSPS.
    \end{itemize}
    \item
    \bcode{./Quantitative/}
    \begin{itemize}
        \item
        \bcode{./Results/}: contains all the results and figures.
        \item
        \bcode{./twosectors.m}: computes the equilibrium of the two-sector model with perfect substitution used in the main text and saves the results in \bcode{.mat} format.
        \item
        \bcode{./fcn2.m}: computes the excess demand at a given vector of price; called by \bcode{twosectors.m}.
        \item
        \bcode{./compute\_tables.m}: computes the raw data used to calculate Tables 4, 5 and 6 in the main text.
        \item
        \bcode{./plot\_figures.m}: plots Figures 5 and 6 in the main text.
        \item
        \bcode{./twosectors\_ces.m}: computes the equilibrium of the two-sector model with constant elasticity of substitution used in Appendix J and saves the results in \bcode{.mat} format.
        \item
        \bcode{./fcnces.m}: computes the excess demand at a given vector of price; called by \\
        \bcode{twosectors\_ces.m}.
        \item
        \bcode{./compute\_tables\_ces.m}: computes the raw data used to calculate Tables J.1 in Appendix J.
        \item
        \bcode{./misc.m}: draws Figure D.2 and computes the decomposition in Sections \rom{4}.A and \rom{4}.B of the main text.
    \end{itemize}
\end{itemize}

@@

The NGSPS comes by 5 \textsc{Stata} \code{.dta} files. \bcode{keynum.dta} contains the information of the key sources, while \bcode{reg1.dta} to \bcode{reg4.dta} host the information of the regular sources. There are 4 files for the regular sources because of the technical limitation back when we initially applied for the data. It is likely that the reader will get one file for the regular source at this moment. These files should be placed under \bcode{./Empirical/Data/}. Executing \bcode{cpsc\_raw.do} will combine the four \bcode{regx.dta} to \bcode{regall.dta} and label all the variables in \bcode{keynum.dta} and \bcode{regall.dta}. It also generates another file \bcode{allfirms.dta} where the two files are combined. All three files are saved under \bcode{./Empirical/Data/}.

Our copy of the CNEC has two \textsc{Stata} \code{.dta} files. \bcode{cec2004\_large\_full.dta} holds those samples that overlap with the commonly used 2004 Annual Surveys of Industrial Firms (ASIF), while \bcode{cec2004\_small.dta} contains small firms not surveyed in the annual ASIF. Again, they should be placed under \bcode{./Empirical/Data/}. The file \bcode{cec\_clean.do} labels all the variables. Upon completion, the original un-labeled files will be replaced by files with the same name.

With these two steps completed, the reader needs to convert the data from \textsc{Stata} \code{.dta} format to the internal binary \code{R} format \code{.RData}. The file \bcode{cpsc\_convert.R} converts \bcode{keynum.dta} to \bcode{KEYFIRM\_R.RData}, \bcode{regall.dta} to \bcode{REGFIRM\_R.RData} and \bcode{allfirms.dta} to \bcode{ALLFIRM\_R.RData}. Similarly, \bcode{cec\_convert.R} converts \\ \bcode{cec2004\_small.dta} to \bcode{DSMALL\_R.RData}, \bcode{cec2004\_large\_full.dta} to \bcode{DLARGE\_R.RData}. It then extracts only the variables used in the paper and combines the two \code{.RData} files to one file \bcode{CNEC\_avgp.RData}. All the files are saved under \bcode{./Empirical/Data/} as before.

@@

In what follows, we will only use the files converted by \code{R}. A list of the essential files is provided below. All the files should be placed under \bcode{./Empirical/Data/}. For ease of reference, we use the two-letter acronyms in parenthesis when referring to the data files later.
\begin{itemize}
    \item
    \bcode{KEYFIRM\_R.RData (PK)}: Key sources of the NGSPS.
    \item
    \bcode{ALLFIRM\_R.RData (PA)}: All sources of the NGSPS.
    \item
    \bcode{CNEC\_avgp.RData (CA)}: All samples in the CNEC.
    \item
    \bcode{DLARGE\_R.RData (DL)}: A subset of \code{CA} which overlaps with the 2004 ASIF.
    \item
    \bcode{susb04.csv (US)}: SUSB 2004.
\end{itemize}

@@

We try to organize our source code by sections in the paper as much as we can. This is not always possible though (or creates unnecessary confusion). We do, however, break the code by sections within the file, where tasks that are reasonably connected logically are grouped together. The code is written such that each section is self-contained, so the readers do not have to run from the very beginning if she/he only wants to replicate a certain result.\footnote{That said, the readers should always check to ensure that all the functional packages of \code{R} are loaded.} Table \ref{tab:navi_main} summarizes the correspondence between the results in the paper (tables, figures, regression results, in-text numbers, etc.) and the section of code files that computes them, as well as data dependency. To further assist the readers to visually navigate through the code, important code snippets are always indicated by a 76-character line of \code{=}. This is the longest line in all the source code, and should be those most visually noticeable amongst all.

@@

    Table 1 is produced by the first part of \bcode{Descriptive.R}. All the numbers are printed to the terminal. Row 1 comes first, with Rows 2 and 3 follow in order.

@@

    Regressions (2), (3), and the un-numbered one in Section \rom{1}.B part \textit{The Role of End-of-pipe Treatment Technologies}, as well as Table 2 are produced by Section 2 of \bcode{Empirical\_AEJ.R}. As one exception, Section 2 relies on Section 1 of \bcode{Empirical\_AEJ.R}. The information in Table 2 is printed to the terminal in the order of Columns 2, 1, 3 and 4. The numbers in Columns 1 and 2 are directly taken from the output. Columns 3 and 4 are calculated by normalizing the physical equipment level to 100. Regression results are then printed to the terminal: first the unnumbered regression, with those of Regressions (2) and (3) follow in order.

@@

    The in-text number of the accounting exercise can be calculated from the results when executing \bcode{Accounting.R}. The 33\% reduction in the last paragraph of Section \rom{1}.C part \textit{An Accounting Exercise} can then be calculated as the weighted average of the variable \bcode{ppar} with Row 1 of Table 1 being the weight. Notice that the variable \bcode{ppar} is exactly Row 3 of Table F.1. Because according to Row 1 of Table 1, the five industries combined contribute to 77\% of total COD emission, assuming that industries emitting the other 23\% COD remain intact, the 25\% reduction in average intensity is simply calculated as $1 - (67\% \times 77\% + 100\% \times 23\%) \triangleq 25\%$.

@@

    To compute the quantitative results, the reader would need to execute \bcode{twosectors.m} several times. There are four cases to be computed: the benchmark case, the no distortion case, the regulation case and the flat tax case. The reader needs to manually set the parameters in \bcode{twosectors.m} for each cases, namely for the distortions \code{tauzd, tauzc}, the regulation intensity \code{xi} and the file name at the very end. The code is tuned to compute and save the benchmark results initially. The code contains all the relevant statements. Hence the reader only needs to comment and un-comment the relevant sections, which should be very easy to locate by searching the variable name.

@@

        Execute \bcode{twosectors.m}. Some information would be printed to the terminal. Please refer to the log file \bcode{quantitative\_main\_log.pdf} for details. The results are saved in \\ \bcode{./Quantitative/Results/benchmark\_new.mat}.

@@

        Set \code{tauzd} and \code{tauzc} back to the benchmark level, change \code{xi} to 0.355, and the export destination to \bcode{./Results/regulation\_new.mat}. The results will be saved in this file after execution. This case is labeled as Case (ii) in the paper.

@@

        Set \code{tauzd} and \code{tauzc} to the flat tax level, reverse \code{xi} back to 0.23, and set the export destination to \bcode{./Results/flattax\_new.mat}. The results will be saved in this file after execution. This case is labeled as Case (i') in the paper.

@@

    Tables 4, 5 and 6 are calculated using the output of \bcode{compute\_tables.m}. Notice that Tables 4 and 6 are presented in relative changes and share a similar structure. By changing the input files at the beginning of \bcode{compute\_tables.m} (in particular the 4 \code{.mat} just computed), \bcode{compute\_tables.m} prints the raw data of the corresponding entries in the same structure as the tables in the paper. Table 5 can be directly taken from the output \code{Table 5} after executing \bcode{compute\_tables.m} with the input being the corresponding cases. Entries in Table 4 can be calculated from the \code{Table 4} of the benchmark case and Cases (i) and (ii), while that of Table 6 can be calculated from \code{Table 4} of the benchmark case and Case (i'). The calculations of the relative changes are not automated, and the reader does have to do the calculations manually as we did. We apologize for the inconvenience.

    The in-text decomposition of total reduction to the contribution of size distribution and technology adoption can be performed using \bcode{misc.m}. The reader needs to change the second input file to either \bcode{notax\_new.mat} or \bcode{regulation\_new.mat}, depending on the case to compute. The role of technology adoption is printed to the terminal, with the residual being that from the size distribution.
    \item
    Several calibration targets are computed from the data as well. This last bulletin point explains where they are computed.
    \begin{itemize}
        \item
        The share of firms using clean technology 57\% is calculated in Section 2 of \bcode{Empirical\_AEJ.R}. The variable \code{clean\_share} hosts the number.
        \item
        The average adoption cost of clean technology as a ratio of output for clean firms 2.5\% is calculated at the end of Section 2 of \bcode{Empirical\_AEJ.R}. The number is printed to the terminal directly.
        \item
        The value of $\phi_1$ is computed in the first part of Section 4 of \bcode{Empirical\_AEJ.R}. The variable \code{phi\_quant} carries the information.
        \item
        The firm size and employment distributions [the light (yellow) bars in Figure 5] are computed at the end of Section 3 of \bcode{Empirical\_AEJ.R}. The variable \code{distchn} is first used to save the employment distribution and then the firm size distribution.
    \end{itemize}
\end{enumerate}

@@

\begin{table}[t]
\footnotesize
\centering
\begin{threeparttable}
\caption{Navigating the Appendix}
\begin{tabular}{llll}
    \hline \hline
    Content                         & File Name                       & File Dependency          & Location in Code \\
    \midrule
    \textbf{Appendix A.1} \\
    \ \ \ Table A.1                 & \bcode{Descriptive.R}           & \code{PK, PA} \\
    \textbf{Appendix B} \\
    \ \ \ Figure B.1                & \bcode{Empirical\_Appendix.R}   & \code{PK, PA, DL, CA}    & Section 1  \\
    \textbf{Appendix C.1} \\
    \ \ \ Figure C.1                & \bcode{Empirical\_Appendix.R}   & \code{PK}                & Section 2  \\
    \ \ \ Table C.1                 & \bcode{Empirical\_Appendix.R}   & \code{PK}                & Section 2  \\
    \ \ \ Figure C.2                & \bcode{Empirical\_Appendix.R}   & \code{PK}                & Section 2  \\
    \ \ \ Regressions (!\#)         & \bcode{Empirical\_Appendix.R}   & \code{PK}                & Section 2  \\
    \ \ \ 3-Regressions (!\#)       & \bcode{Empirical\_AEJ.R}        & \code{PK}                & Section 2 \\
    \textbf{Appendix D.1} \\
    \ \ \ Figure D.1                & \bcode{Empirical\_Appendix.R}   & \code{CA}                & Section 4  \\
    \ \ \ Figure D.2                & \bcode{misc.m}                  & \code{*.mat} \\
    \textbf{Appendix D.2} \\
    \ \ \ Table D.1                 & \bcode{Empirical\_Appendix.R}   & \code{PK}                & Section 3  \\
    \ \ \ Regression (!\#)          & \bcode{Empirical\_Appendix.R}   & \code{PK}                & Section 3  \\
    \ \ \ Fixed Cost Ratio          & \bcode{Empirical\_Appendix.R}   & \code{PK}                & Section 3  \\
    \textbf{Appendix E.1} \\
    \ \ \ Figure E.1                & \bcode{Empirical\_Appendix.R}   & \code{CA, US}            & Section 5  \\
    \textbf{Appendix F} \\
    \ \ \ Table F.1                 & \bcode{Accounting.R}            & \code{PK, CA, US}  \\
    \textbf{Appendix J} \\
    \ \ \ Table J                   & \bcode{twosectors\_ces.m}       & \multirow{2}{*}{\centering \code{*.mat}} \\
                                    & \bcode{compute\_tables\_ces.m} \\
    \bottomrule
\end{tabular}
\label{tab:navi_appendix}
\begin{tablenotes}
     \footnotesize{
     \item[$\dagger$]
     Acronyms for datasets:
     \begin{itemize}[leftmargin=*]
        \item
        \bcode{KEYFIRM\_R.RData (PK)}: Key sources of the NGSPS.
        \item
        \bcode{ALLFIRM\_R.RData (PA)}: All sources of the NGSPS.
        \item
        \bcode{CNEC\_avgp.RData (CA)}: All samples in the CNEC.
        \item
        \bcode{DLARGE\_R.RData (DL)}: A subset of \code{CA} which overlaps with the 2004 Annual Surveys of Industrial Firm.
        \item
        \bcode{susb04.csv (US)}: SUSB 2004.
     \end{itemize}
     }
     \item[$\ddag$]
     All the \code{*.mat} files will be produced by \bcode{twosectors\_ces.m}.
     \item[$\diamondsuit$]
     Notation (!\#) stands for ``un-numbered.''
\end{tablenotes}
\end{threeparttable}
\end{table}

\begin{enumerate}
    \item
    Table A.1 is produced by the second part of \bcode{Descriptive.R}. All numbers are printed to the terminal.
    \item
    Figure B.1 is generated by Section 1 of \bcode{Empirical\_Appendix.R}. The four panels are saved respectively as \bcode{./Empirical/Results/FigureB1\_TopLeft.pdf}, \bcode{FigureB1\_TopRight.pdf}, \\ \bcode{FigureB1\_BotLeft.pdf} and \bcode{FigureB1\_BotRight.pdf}.
    \item
    Section 2 of \bcode{Empirical\_Appendix.R} produces the results in Appendix C.1. The beginning of that section first runs the regression of intensity to size by industry. The regression results are printed to the terminal, which are exactly the results reported in Table C.1. The five panels of Figure C.1 are then exported to \bcode{./Empirical/Results/} with the names \bcode{FigureC1\_TopLeft.pdf}, \\ \bcode{FigureC1\_TopRight.pdf}, \bcode{FigureC1\_MidLeft.pdf}, \bcode{FigureC1\_MidRight.pdf} and \\ \bcode{FigureC1\_BotLeft.pdf}. Notice that the bottom-right panel is simply Figure 1 in the main text. The code then repeats the exercise for the manufacturing sector as a whole. Results of the un-numbered regressions on Pages 9 and 10 (the last one) are then printed to the terminal, with Figure C.2 exported to \bcode{./Empirical/Results/FigureC2.pdf}.
